---
title: "R Notebook"
output: html_notebook
---

# Video game sales project: data exploration

```{r}
library(tidyverse)
library(janitor)

all_sales <- read_csv("data/sales-2019.csv") %>% 
  clean_names()

ps4_sales <- read_csv("data/ps4-game-sales.csv") %>% 
  clean_names()

xbox_sales <- read_csv("data/xbox-one-game-sales.csv") %>% 
  clean_names()

nin_sales <- read_csv("data/nintendo_sales.csv") %>% 
  clean_names()

extra_sales <- read_csv("data/extra_videogame_sales.csv") %>% 
  clean_names()

all_sales
```

```{r}
all_sales %>% 
  skimr::skim()
```

```{r}
ps4_sales
```

```{r}
skimr::skim(ps4_sales)
```

```{r}
xbox_sales
```

```{r}
skimr::skim(xbox_sales)
```

```{r}
skimr::skim(extra_sales)
```

```{r}
total_user_score_extra <- 16719 - 6704
total_critic_score_extra <- 16719 - 8582
total_user_score_all <- 55792 - 55497
total_critic_score_all <- 55792 - 49296

total_critic_score_all
total_critic_score_extra
```
extra sales has more critic scores

```{r}
total_user_score_all
total_user_score_extra
```
extra sales has more user scores

```{r}
extra_sales
```

### extra_sales may be more useful than our original dataset (all_sales)


```{r}
skimr::skim(all_sales)
skimr::skim(extra_sales)
```

sales columns: extra
critic score: extra
user score: extra

our measurements of success for a game have more values in the extra sales data, all sales may have more of other values but these are meaningless if we don't have a measurement for how successful the game is. Therefore extra_sales will be more useful.

```{r}
GGally::ggcorr(extra_sales)
```

the correlation between sales and critic score is weak, therefore we will keep both in as metrics of success instead of using just one.

```{r}
all_sales %>% 
  filter(year > 2016 & is.na(global_sales) == FALSE)
```

The original data has games after 2016, but the new data doesn't. We can join these!