---
title: "R Notebook"
output: html_notebook
editor_options: 
  chunk_output_type: inline
---

```{r}
library(tidyverse)
library(GGally)
library(ggfortify)
library(modelr)
library(glmulti)

vg_sales <- read_csv("vg_sales.csv") %>%
  select(-name, -developer, -publisher, -year_of_release, -...1) %>% 
  filter(platform %in% c("Nintendo", "Sony Playstation", "PC", "Microsoft Xbox")) %>% 
  drop_na(platform, genre) %>% 
  mutate(rating = coalesce(rating, "Unknown"))
  
ggpairs(vg_sales)
```

# model 1: with sales variables

```{r}
alias(lm(global_sales ~ ., data = vg_sales))
```
```{r}
n_data = nrow(vg_sales)
test_index <- sample(1:n_data, size = n_data*0.1)
sales_test <- slice(vg_sales, test_index)
sales_train <- slice(vg_sales, -test_index)
```

```{r}
ceiling <- lm(global_sales ~ ., data = sales_train)

summary(ceiling)
```

```{r}
glmulti(global_sales ~ ., data = vg_sales, method = "h")
```
Best model: global_sales~1+other_sales:eu_sales+other_sales:jp_sales+rating:platform+rating:na_sales+rating:eu_sales+rating:jp_sales+rating:other_sales

```{r}
mod_best <- lm(global_sales~1+other_sales:eu_sales+other_sales:jp_sales+rating:platform+rating:na_sales+rating:eu_sales+rating:jp_sales+rating:other_sales, data = vg_sales)

autoplot(mod_best)
```

```{r}
mod1a <- lm(global_sales ~ na_sales, data = sales_train)
mod1b <- lm(global_sales ~ eu_sales, data = sales_train)

summary(mod1a)
summary(mod1b)
```

```{r}
autoplot(mod1a)
```
Pass

```{r}
mod2a <- lm(global_sales ~ na_sales + eu_sales, data = sales_train)
mod2b <- lm(global_sales ~ na_sales + genre, data = sales_train)

summary(mod2a)
summary(mod2b)
```

```{r}
autoplot(mod2a)
```

```{r}
mod3a <- lm(global_sales ~ na_sales + eu_sales + other_sales, data = sales_train)
mod3b <- lm(global_sales ~ na_sales + eu_sales + jp_sales, data = sales_train)

summary(mod3a)
summary(mod3b)
```

```{r}
autoplot(mod3b)
```

```{r}
mod4a <- lm(global_sales ~ na_sales + eu_sales + jp_sales + other_sales, data = sales_train)
mod4b <- lm(global_sales ~ na_sales + eu_sales + jp_sales + platform, data = sales_train)

summary(mod4a)
summary(mod4b)
```

mod4b has a perfect r squared meaning it predicts with 100% accuracy, this makes sense as the different sales areas will always add up to global_sales

```{r}
mod_test <- lm(global_sales ~ na_sales + eu_sales + jp_sales + other_sales, data = sales_test)

summary(mod_test)
```
r squared test = rsquared train: meaning the model is well fit

# Model 2 - without sales

```{r}
vg_sales_trim <- vg_sales %>% 
  select(-jp_sales, -other_sales, -eu_sales, -na_sales)

n_data2 = nrow(vg_sales_trim)
test_index2 <- sample(1:n_data2, size = n_data2*0.1)
sales_test2 <- slice(vg_sales_trim, test_index2)
sales_train2 <- slice(vg_sales_trim, -test_index2)
```

```{r}
ceiling2 <- lm(global_sales ~ ., data = vg_sales_trim)

summary(ceiling2)
```

r squared = 0.02: This model would not predict much of anything

Due to the nature of the variables, this data is not fit for modelling. We do now know that the sales area have importance in the following order: NA, EU, JP, Other